Team size and composition in home health care

### 2023-10-25 paper-presentation/paper-presentation.qmd
Added slide for principle 4

::: {.r-fit-text}
For some grade of service [$\gamma$]{style="color: red;"}, the required weekly capacity [$C$]{style="color: red;"} is $$C = \rho + \gamma z \rho$$

@@

@@

::: columns
::: {.column width="75%"}

```{python}
#------------------------------------------------------------------------------
# Principle 4: team composition
#------------------------------------------------------------------------------

@@

# 'Optimal' team-composition
::: columns
::: {.column width="50%"}
$$\lambda_1\frac{\mathbb{E}[N]}{C}+\lambda_3\mathbb{P}(P \le l)−\lambda_4 ∑_{k∈Q}(\frac{C_k}{∑_{j∈Q}C_j}- \frac{\mu_k}{∑_{j∈Q}\mu_j}) −\lambda_6\frac{M(M−1)}{2}$$
:::

>>>>

::: r-fit-text
For some grade of service [$\gamma$]{style="color: red;"}, the required weekly capacity [$C$]{style="color: red;"} is $$C = \rho + \gamma z \rho$$

@@

## Principle 4: Team composition
::: r-fit-text
$$
min \sum\limits_{k∈Q} w_kC_k\\
s.t. C_k + e_k ≥ μ_k + η_ασ_k, ∀k ∈ Q,\\
C_k ∈ {0}∪[l,∞), ∀k ∈ Q,\\
$$
Where:

- $Q = \{1,2,...,K\}, K ∈ N$, is a set of qualification levels with an ordering such that capacity of QL $k$ can be deployed to cover demand of all QLs $j≤k$ as well.

- $N_k$ is the required demand for QL $k∈Q$ in a given week and $N_k$ is normally distributed with mean $μ_k$ and variance $σ_k^2$.
- $C_k ≥ 0$ is the capacity of QL $k$ deployed over the given week.

- Each unit of capacity of QL $k$ comes at a cost $w_k ≥ 0$, with $w_j ≤ w_k$, if $j ≤ k$.

- Due to the minimum size of contracts, if capacity of QL $k$ is used (i.e., $C_k > 0$), then the corresponding capacity should at least be $l$ units.
:::

@@

::: columns
::: {.column width="75%"}
```{python}
#------------------------------------------------------------------------------
# Principle 4: team composition
#------------------------------------------------------------------------------

@@

# 'Optimal' team-composition

::: columns
::: {.column width="50%"}
$$\lambda_1\frac{\mathbb{E}[N]}{C}+\lambda_3\mathbb{P}(P \le l)−\lambda_4 ∑_{k∈Q}(\frac{C_k}{∑_{j∈Q}C_j}- \frac{\mu_k}{∑_{j∈Q}\mu_j}) −\lambda_6\frac{M(M−1)}{2}$$
:::
